RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-14 paper.tex
worked on requirements

>>>>

\todo{Define the requirements for the system}
\begin{itemize}
\item Technology transfer. Things developed by analysts need to become accessible in the production environment and should be supported in the environment, making it easy to push new features, experiments, etc.
\item Dasboarding. There should be a mode in which people can operate the experiments without coding. At times code has to be written because some things cannot be done any other way but other people must not ever see code because their eyes will fall out.
\item Version control as a primary concept in the repository. Need to control the visibility of 
\item Modern interactive technologies. People want to interact with data to explore it. Scalable technologies like crossfilter exist. Want to support those in the context of an R environment. Need to support full 2-way communication between computing in the cloud and interaction on the web.
\item Other requirements e.g. Kandel's user study. Not our contribution but things we must address, mentioned in related work section. Heer/Agarwala design considerations for collaborative visual analytics.
\end{itemize}
